\documentclass[a4paper,11pt]{article}
\usepackage{graphicx}


%opening
\title{Course2012 Assignment 7}
\author{Institute of Computing Technology, \\
                       Chinese Academy of Sciences, Beijing, China }

\begin{document}

\maketitle

Notice:\\\\
1. Due Jan. 4,  2013.\\
2. Please hand in your answer in hard copy.\\
3. You can choose two problems from Problem 1-6.\\
4. You can present your answer in English or in Chinese.\\\\
The following problems can be used for your reduction to prove NP-completeness: \\
{\sc SAT}, {\sc 3SAT}, {\sc Independent-Set}, {\sc Vertex-Cover}\\
{\sc 3-Coloring}, {\sc Set-Cover}, {\sc Subset-Sum}, {\sc Hamilton-Cycle}\\
% \section{P class (10 marks)}
% 
% Let {\sc 2SAT} be the set of satisfiable boolean formulas in $SAT$ with exactly $2$ literals per clause. Show that $2SAT\in P$.\\

\section{NP-completeness}

The {\sc subgraph-isomorphism} problem takes two graphs $G_1$ and $G_2$ and asks whether $G_1$ is isomorphic to a subgraph of $G_2$. Show that the subgragh-isomorphism problem is NP-complete.

\section{NP-completeness}

Given an integer $m\times n$ matrix $A$ and an integer $m$-vector $b$, the {\sc 0-1 integer-programming} problem asks whether there is an integer $n$-vector $x$ with elements in the set $\{0,1 \}$ such that $Ax\geq b$. Prove that 0-1 integer programming is NP-complete.

\section{NP-completeness}

The {\sc set-partition} problem takes as input a set $S$ of numbers. The question is whether the numbers can be partitioned into two sets $A$ and $B$ and $B = S-A$ such that $\Sigma_{x\in A} x=\Sigma_{x\in B} x$. Show that the set-partition problem is NP-complete.

\section{NP-completeness}

In the {\sc half-3SAT} problem, we are given a 3SAT formula $\phi$ with $n$ variables and $m$ clauses, where $m$ is even. We wish to determine whether there exists a truth assignment to the variables of $\phi$ such that exactly half the clauses evaluate to $0$ and exactly half the clauses evaluate to $1$. Prove that the {\sc half-3SAT} problem is NP-complete.

\section{NP-completeness}

Show that {\sc Undirected-Hamilton-Cycle} problem is NP-complete.\\
{\sc Undirected-Hamilton-Cycle(decision problem)}:\\
{\bf Input:} an undirected gragh $G$\\
{\bf Output:} 1 if $G$ has a Hamilton cycle which visits each vertex exactly once and also returns to the starting vertex, 0 for others\\

\section{NP-completeness}
Given a directed graph $G = (V, E)$, a path cover is a set of directed paths such that every vertex $v \in V$ belongs to exactly one path.
The {\sc minimum path cover} problem consists of finding a path cover for $G$ having at most $k$ paths. To prove that the {\sc minimum path cover} problem is NP-complete.


\end{document}
