\documentclass[a4paper,11pt]{article}
\usepackage{graphicx}


%opening
\title{CS612 Assignment 5}
\author{Institute of Computing Technology, \\
                       Chinese Academy of Sciences, Beijing, China }

\begin{document}

\maketitle

Notice:\\\\
1. Due Dec. 17, 2009.\\
2. Please send your answer to wangchao1987@ict.ac.cn, shaomingfu@gmail.com, yuanxiongying@ict.ac.cn\\
3. You can arbitrarily choose two problems from Problems 1-5.
\section{Greedy Algorithm(5 marks)}
Let us say that a graph $G=(V,\ E)$ is a $near-tree$ if it is connected and has at most $n+8$ edges, where $n=|V|$. Give an algorithm with running time $O(n)$ that takes a near-tree $G$ with costs on its edges, and returns a minimum spanning tree of $G$. You may assume that all the edge costs are distinct.

\section{Greedy Algorithm(10 marks)}
Given a list of $n$ natural numbers $d_1$, $d_2$,...,$d_n$, show how to decide in polynomial time whether there exits an undirected graph $G=(V,\ E)$ whose node degrees are precisely the numbers $d_1$, $d_2$,...,$d_n$. $G$ should not contain multiple edges between the same pair of nodes, or `` loop" edges with both endpoints equal to the same node.

\section{Greedy Algorithm(10 marks)}
Suppose you are given a directed graph $G=(V,\ E)$ in which each edge has a cost of either $0$ or $1$. Also suppose that $G$ has a node $r$ such that there is a path from $r$ to every other node in $G$. You are also given an integer $k$. Give a polynomial-time algorithm that either constructs an arborescence rooted at $r$ of cost {\bf exactly} $k$, or reports that no such arborescence exists.

\section{Greedy Algorithm(10 marks)}
The input consists of $n$ skiers with heights $p_1$, $p_2$,...,$p_n$, and $n$ skies with height $s_1$, $s_2$,...,$s_n$. The problem is to assign each skier a ski to minimize the {\bf AVERAGE DIFFERENCE} between the height of a skier and his/her assigned ski. That is, if the skier $i$ is given the ski $a_i$, then you want to minimize:$${\Sigma}_{i=1}^n (|p_i-s_{a_i}|)/n$$

\section{Greedy Algorithm(10 marks)}
The input to this problem consists of an ordered list of $n$ words. The length of the $i$th word is $w_i$, that is the $i$th word takes up $w_i$ spaces. The goal is to break this ordered list of words into lines, this is called a layout. Note that you can not reorder the words. The length of a line is the sum of lengths of the words on that line. The ideal line length is $L$. No line may be longer than $L$, although it may be shorter. The penalty of having a line of length $K$ is $L-K$. The total penalty is the {\bf sum} of the line penalties. The problem is to find the layout that minimizes the total penalty.

\end{document}
